An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-29 draft.tex
Exp1 results

@@

The

\begin{figure}[h!tb]
  % Is the axis correct? Seconds per instance or total time? Please
  % change that - JJ
  % Yes, they are instances - Mario
    \centering
    \includegraphics[width=\textwidth]{sp_size_worker}
    \caption{Time required, in seconds, to complete an instance of the function, with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{sp_size_worker}
    \caption{Time required, in seconds, to complete an instance of the function, with different number of workers and populations sizes }
    \label{fig:spworker}
\end{figure}

@@

We summarize the results of the experiment in Figure \ref{fig:spworker}.  The
experiment consisted of executing the same benchmark on EvoSwarm twice but
changing the number of populations used in each run. The left column has the
results when using five populations, and the right side shows the results for
ten.  Graphics show the execution time achieved by a certain number of workers.
Each box-plot indicates the time required for the execution of 15  function
instances, in seconds.  Each row has a different scale on the y-axis, to
compensate for the dimension increments. It is important to notice that the
execution time can also be affected by the algorithm finding a solution with an
error smaller than the threshold, before completing all the FEs.

As expected, in most cases, increasing the number of workers reduces the time
required for the execution of an instance. Mainly when using the same parameters
(number of populations and number of workers ). But, when we compare the two
options, we find some subtle differences:

When using one or two workers, using 5 populations is better in most cases. A
reason for this could be that the migration of individuals takes more time to
reach the worker. For instance, when a single worker has 10 populations, only
after processing all, it will start receiving mixed populations.  Although, in
all cases, and even a single worker, populations are heterogeneous, this
advantage takes more time to propagate. With four workers, almost the same
results can be achieved regardless of our selection between five or ten
populations. Also, there is no much difference between 4 and 8 workers, when
using five populations. In general, we can observe that keeping a ratio close to
1:1 between the number of workers and populations exploits better the computing
resources available.
